\subsection{Views}

We are tasked with creating a script that creates two views, with two \verb`select`, \verb`insert`, \verb`update`, and \verb`delete` statements for each of the views.

\subsubsection{Users view without passwords}

The first view that we made is called \verb`users_passwordless` and it is essentially the users table, but without the hashed passwords column. Its purpose is to maintain this sensitive information away from some of the less trusted employees at Ask Us who have no need to access it.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/users\_passwordless/users\_passwordless.sql}]{../sql/views/users_passwordless/users_passwordless.sql}

Below are two \verb`select` statements which retrieve data from the view.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/users\_passwordless/select.sql}]{../sql/views/users_passwordless/select.sql}

Then we ran these two insert statements on the view. As expected, they did not succeed, and yielded the error message below.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/users\_passwordless/insert.sql}]{../sql/views/users_passwordless/insert.sql}

\begin{verbatim}
	ORA-01400: cannot insert NULL into ("AMURCIAN","USERS",
	"PASSWORD")
\end{verbatim}

Next, we tried to update the username of one user and the email of another with the following commands. These completed successfully.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/users\_passwordless/update.sql}]{../sql/views/users_passwordless/update.sql}

Finally we tried to remove two users from the view. We first had to find some users who were not referenced by a foreign key. Here are the commands we used to delete them.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/users\_passwordless/delete.sql}]{../sql/views/users_passwordless/delete.sql}

\subsubsection{Combination of all different post types}

The second view is intended to combine all the posts, with their content into one `table' \verb`all_posts`.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/all\_posts/all\_posts.sql}]{../sql/views/all_posts/all_posts.sql}

We have written the following two \verb`select` statements to test this view.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/all\_posts/select.sql}]{../sql/views/all_posts/select.sql}

We also ran a couple of insert statements on this view, expecting it to fail. Indeed we saw this error message.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/all\_posts/insert.sql}]{../sql/views/all_posts/insert.sql}

\begin{verbatim}
	ORA-01732: data manipulation operation not legal on this view
\end{verbatim}

Next we ran two update commands, as shown below, but of course, we received the same error.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/all\_posts/update.sql}]{../sql/views/all_posts/update.sql}

Finally, we tried to delete some rows from the view, but once again, we received the same error as above.

\VerbatimInput[label=\fbox{\color{Black}/sql/views/all\_posts/delete.sql}]{../sql/views/all_posts/delete.sql}